A New Metric for the Analysis of Swarms that are modelled using potential fields

### 2018-08-05 paper.tex
More Updates

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5cm]{figures/StabilityNullVector}
{Equilibrium with null vectors.\label{methods:StabilityNullVector}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=5.5cm]{figures/StabilityNullVector3}
{(t).\label{concave:VoidPerimeter1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=6cm]{figures/StabilityNullVector2}
{(t + 1).\label{concave:VoidPerimeter2}}

@@

% \section{Calculating distance internal movement}
Equation~(\ref{eq:SwarmStabilityDistance1}) computes the mean distance of an agent to its neighbours $nbr(b)$. 
%% The relative position vector generated for an agent $b$ to its neighbour $b'$, $bb'$, is shown in~(\ref{eq:FlyToCentre1}). The magnitude of that vector gives the distance between two agents. For an individual agent the average magnitude $\mu_d(b)$ is calculated as \ref{eq:SwarmStabilityDistance1} where $b$ is the agent and $|nbr(b)|$ is the number of neighbours.

@@

The two metrics together provide a deeper evaluation of a swarm's structure and `potential' than either of the metrics alone. Consider the following: the repulsion field is increased but the internal distances do not change; as a result the \emph{cohesion/repulsion metric} falls below zero. This indicates `something' is confining the swarm's distribution as discussed in Section \ref{metric:ApplicationFloodFilling}. This analysis could be used in identifying effective swarm distribution for the coverage of a sensor array as discussed by Ramaithitima et al.~\cite{RWBK:15}

@@

\section{Future work}\label{Section:FutureWork}
The new metric can be applied to the analysis of the effects of coordination
algorithms upon a swarm's structure. An application to flood filling has
been discussed~(Section~\ref{metric:ApplicationFloodFilling}). The metric can also be applied to identifying the effects of 
`healing' algorithms, e.g. to remove `voids' from a swarm. We plan
to investigate this, and other, practical applications of the metric.

>>>>

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4cm]{figures/StabilityNullVector}
{Equilibrium with null vectors.\label{methods:StabilityNullVector}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4cm]{figures/StabilityNullVector3}
{Equilibrium with directional vector (t).\label{concave:VoidPerimeter1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4cm]{figures/StabilityNullVector2}
{Equilibrium with directional vector (t + 1).\label{concave:VoidPerimeter2}}

@@

% \section{Calculating distance internal movement}
Equation~(\ref{eq:SwarmStabilityDistance1}) calculates the mean distance of an agent to its neighbours $nbr(b)$. 
%% The relative position vector generated for an agent $b$ to its neighbour $b'$, $bb'$, is shown in~(\ref{eq:FlyToCentre1}). The magnitude of that vector gives the distance between two agents. For an individual agent the average magnitude $\mu_d(b)$ is calculated as \ref{eq:SwarmStabilityDistance1} where $b$ is the agent and $|nbr(b)|$ is the number of neighbours.

@@

The two metrics together provide a deeper evaluation of a swarm's structure and `potential' than either of the metrics alone. Consider the following: the repulsion field is increased but the internal distances do not change; as a result the \emph{cohesion/repulsion metric} falls below zero. This indicates `something' is confining the swarm's distribution as discussed in Section \ref{Section:ApplicationFloodFilling}. This analysis could be used in identifying effective swarm distribution for the coverage of a sensor array as discussed by Ramaithitima et al.~\cite{RWBK:15}

@@

\section{Future work}\label{Section:FutureWork}
The new metric can be applied to the analysis of the effects of coordination
algorithms upon a swarm's structure. An application to flood filling has
been discussed~(Section~\ref{Section:ApplicationFloodFilling}). The metric can also be applied to identifying the effects of 
`healing' algorithms, e.g. to remove `voids' from a swarm. We plan
to investigate this, and other, practical applications of the metric.
